Contracts for Contracts

### 2023-05-08 paper/introduction.tex
intro

Apart from the investigating effort to certify and verify smart contract
programs, language designers are responsible to empower programmers with better
linguistic solutions to secure smart contracts in the first place.
In this paper, we develop practical \emph{higher-order and temporal behavioral
software contracts} that provide a lightweight solution for securing
\emph{smart contracts}.

\subsubsection*{\textbf{Behavioral Contracts for Smart Contracts}}
Behavioral contracts provide a mechanism for programmers to specify assumptions
and guarantees of software components. The specified assumptions and guarantees
will be monitored and reported when violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
Design-by-Contract methodology \cite{DBLP:conf/tools/Meyer98a}, behavioral
contracts have been widely adopted in Java, Haskell, C\#, Python, Racket,
Elixir \cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \todo{cite}

@@

\subsubsection*{\textbf{Contracts for Callable Addresses and Higher-Order Functions}}
Higher-order contracts provides a way to specify and enforce pre- and
post-conditions of untrusted functions. \todo{...}

@@

\subsubsection*{\textbf{Contracts for Temporal Properties}}
Temporal contracts provides a way to \todo{...}.
\todo{why static verification fails}

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
	\item We propose a specification of behavioral contracts for expressing and
	      enforcing higher-order and temporal properties for smart contracts.
	\item We design \lang, an extension for Solidity with
	      behavioral contracts, demonstrate its use cases through extensive examples,
	      and how it can improve the safety and reliability.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
	\item We examine a number of real-world attacks and show that our proposal is
	      effective in improving safety and reliability.
	\item We implement our approach on top of the existing Solidity compiler and shows
	      that its runtime overhead is marginal, therefore practical to use.
	\item \zz{Would open-sourcing be considered a contribution? Lol}
\end{itemize}

>>>>

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
In this paper, we develop practical \emph{behavioral
software contracts} that provide a lightweight solution for securing
\emph{smart contracts}. In particular, we develop a specification language and
monitor for higher-order and temporal behaviors in the Solidity language.

\subsection*{\textbf{Behavioral Contracts for Smart Contracts}}

Behavioral contracts provide a mechanism for programmers to specify assumptions
and guarantees of software components. The specified assumptions and guarantees
will be monitored and reported when violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
Design-by-Contract methodology \cite{DBLP:conf/tools/Meyer98a}, behavioral
contracts have been widely adopted in Java, Haskell, C\#, Python, Racket,
Elixir \cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \todo{cite}

@@

\subsection*{\textbf{Contracts for Callable Addresses and Higher-Order Functions}}

Higher-order contracts provides a way to specify and enforce pre- and
post-conditions of untrusted functions. \todo{...}

@@

\subsection*{\textbf{Contracts for Temporal Properties}}

Temporal contracts provides a way to \todo{...}.
\todo{why static verification fails}

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We design \lang, an extension for Solidity that allows programmers to
        specify and enforce higher-order and temporal behaviors in smart contracts.
        We demonstrate \lang's use cases through extensive examples and
        implement \lang as a preprocessor for ordinary Solidity programs.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
  \item We examine a number of real-world attacks with \lang, showing that our
        approach is effective in improving safety and reliability of smart contract
        programs.
  \item We evaluate the overhead of \lang compared to manually implemented
        assertions and checks, showing that our approach does not introduce
        additional runtime overhead.
\end{itemize}
\lang is open-sourced and publicly available at \note{url}.
